The Anatomy of a Temporal Summarization System

### 2015-02-27 dataset.tex
edits; nuggets

For the document stream, we use the news portion of the
 2014 Trec KBA Stream Corpus.
The documents from this corpus come from hourly crawls of the web covering 
 ?, 20?? to ?, 20??. \ckcomment{Need to mention we further filtered the corpus}

Our experiments also make use of the Trec Temporal Summarization (TS) Track
 data from 2013 and 2014. 
This data includes 25 events and event metadata (e.g., a user
search query for the event, the event type, and event evaluation timeframe).  
All events occurred during the time span of the Trec KBA Stream Corpus.

>>>>

For the document stream, we use the news portion of the
 2014 TREC KBA Stream Corpus.
The documents from this corpus come from hourly crawls of the web covering 
 ?, 20?? to ?, 20??. \ckcomment{Need to mention we further filtered the corpus}

Our experiments also make use of the TREC Temporal Summarization (TS) Track
 data from 2013 and 2014. 
This data includes 25 events and event metadata (e.g., a user
search query for the event, the event type, and event evaluation timeframe).  
All events occurred during the time span of the TREC KBA Stream Corpus.

### 2015-02-27 experiments.tex
edits; nuggets

NIST developed a series metrics for evaluating update summarization systems
as part of the Trec TS track.
We present results on two of these metrics, the expected gain and 
comprehensiveness.

@@

\subsection{Model Comparisons}

Our proposed model using AP+Salience is compared against several variants and baselines. All thresholds
are tuned on the development set.

@@

\textbf{AP+Salience Time Ranked (AP+SalienceTR)} Our final model is identical 
to the
AP+Salience model except at the novelty filter stage.
Within the novelty filtering stage, 
AP+Salience inspects exemplars in order of decreasing salience when computing
similarity to previous updates. Because the order in which we add updates
affects future similarity calculations, we evaluate an alternate ordering 
scheme (AP+SalienceTR) where exemplars are selected in order of increasing 
time since event start. The purpose of this model is to give preference to 
more recent updates, since timelyness is one of the desirable traits of our update
summaries.

>>>>

NIST developed a series metrics for evaluating update summarization systems
as part of the TREC TS track.
We present results on two of these metrics, the expected gain and 
comprehensiveness.

@@

\subsection{Model Comparisons}
We refer to our complete model as \textbf{AP+Salience}.  We compare this model again several variants and baselines intended to measure the contribution of different components. All thresholds
for all runs are tuned on the development set.

@@

\fdcomment{consider removing AP+SalienceTR}
\textbf{AP+Salience Time Ranked (AP+SalienceTR)} Our final model is identical 
to the
AP+Salience model except at the novelty filter stage.
Within the novelty filtering stage, 
AP+Salience inspects exemplars in order of decreasing salience when computing
similarity to previous updates. Because the order in which we add updates
affects future similarity calculations, we evaluate an alternate ordering 
scheme (AP+SalienceTR) where exemplars are selected in order of increasing 
time since event start. The purpose of this model is to give preference to 
more recent updates, since timelyness is one of the desirable traits of our update
summaries.

### 2015-02-27 introduction.tex
edits; nuggets

In this paper, we present an update summarization system to track events
across time. Our system predicts sentence salience in the context of a
large-scale event, such as a disaster, and integrates these predictions into
a clustering based multi-document summarization system. 
Not only does incorporating salience produce more relevant summaries,
our system is better able to adapt to
dynamic changes in input volume which adversely 
effect methods that use redundancy as a proxy for salience. 
%or predict salience but
%ignore redundancy in the input alone.

In addition to the tight integration between clustering and salience
prediction, our approach also exploits knowledge about the event to determine
salience. Thus, salience does not just represent importance within a set of
documents; it also represents both how typical a sentence is of the  
event
type (i.e., industrial accident, hurricane, riot) and whether it specifies 
information
about this particular event. 
Our feature representation includes a set of language models, one for each
event type, to measure the typicality of the sentence with regard to the 
current event, the distance of mentioned locations from the center of
the event, and the change in word frequencies over the time of the event.
While we ground these features in the domain of disaster, their templates
are generally applicable to many update summarization domains.
% to represent its likelihood of referring to the input disaster. 
%We also utilize the change in word frequencies as we process the stream 
%to measure the changing importance of updates over time.

>>>>

In this paper, we present an update summarization system to track events
across time. Our system predicts sentence salience in the context of a
large-scale event, such as a disaster, and integrates these predictions into
a clustering based multi-document summarization system. 
We demonstrate that combining salience with clustering produces more relevant summaries
compared to baselines using clustering alone.  We believe this is
because our system is better able to adapt to
dynamic changes in input volume which adversely 
effect methods that use redundancy as a proxy for salience. 
%or predict salience but
%ignore redundancy in the input alone.

In addition to the tight integration between clustering and salience
prediction, our approach also exploits knowledge about the event to determine
salience. Thus, salience does not just represent importance within a set of
documents; it also represents both how typical a sentence is of the  
event
type (i.e., industrial accident, hurricane, riot) and whether it specifies 
information
about this particular event. 
Our feature representation includes a set of language models, one for each
event type, to measure the typicality of the sentence with regard to the 
current event, the distance of mentioned locations from the center of
the event, and the change in word frequencies over the time of the event.
While we ground these features in the domain of disaster, this approach is generally applicable to any update summarization task where queries can be categorized by the 
expected similarity of their ideal summaries.
% to represent its likelihood of referring to the input disaster. 
%We also utilize the change in word frequencies as we process the stream 
%to measure the changing importance of updates over time.

### 2015-02-27 methods.tex
edits; nuggets

Our update summarization system takes as input 
\begin{enumerate*}[label=\itshape\alph*\upshape)]
  \item a short query defining the event to be tracked (e.g. `Hurricane Sandy'), 
  \item an event category defining the type of event to be tracked (e.g. `hurricane'), 
  \item a stream of time-stamped documents %, $(\doc_0, \doc_1,\ldots,\doc_T)$,
  presented in temporal order, and \item an evaluation time period of interest.
    %  $(\stime,\etime)$.  
      \end{enumerate*} While processing documents
      throughout the time period of interest, the system outputs sentences,
      which we refer to as updates.
      Updates should not only be relevant to the event but also salient,
      i.e. worthy of
      reporting.
      For most domains, updates also need to be 
      timely and novel, i.e. users need to be informed of changes in the 
      event as quickly as possible.
      Finally, in aggregate the updates must comprehensively summarize the 
      event.

@@

In order to quantify the salience of an update with respect to an event,
we match the update to its most similar event nugget.
%we assume the event can be represented as a set of atomic facts, or nuggets.
Formally, given an update $u$ and a set of nuggets $N$ we define the salience of 
$u$ as,
\[\operatorname{salience}(u) = \operatorname{max}_{n \in N} 
\operatorname{sim}(u, n) \]
where $\operatorname{sim}(\cdot)$ is the semantic similarity such as
the cosine similarity of latent vectors associated with the update and 
nugget text \cite{?}. % We train
% a regression model to predict salience using features derived from
% the updates themselves
% and the document stream.

@@

Our system architecture follows a simple pipeline design where each
stage provides an additional level of processing or filtering of the input
sentences.
We begin with an empty update summary $U$.
At each hour we receive a new batch of sentences $b_t$ from the stream
and perform the following actions:
\begin{enumerate}
    \item predict the salience of sentences in $b_t$ (Section~\ref{sec:salpred}),
  \item select a set of exemplar sentences (by combining clustering with 
      salience predictions) (Section~\ref{sec:exsel}),
  \item add the most novel and salient exemplars to $U$ (Section~\ref{sec:upsel}).
\end{enumerate}

The resultant list of updates $U$ is our summary of the event.
Step 2 uses the affinity propagation algorithm to incorporate the salience
predictions from step 1. We refer to this summarization 
system as the \textbf{AP+Salience} model.

@@

When evaluating our summarization system
we do not have access to event nuggets. However, we can use the nuggets
in our training data to learn a model to predict salience for sentences
from new events.
For each event in our training data, we sample a set of sentences and  each 
sentence's salience is computed, i.e. we compute the maximum semantic 
similarity to the event's nuggets.
We now have a training set of set sentences and the target values 
(their salience) to predict.

@@

@@

\paragraph{Geographic Relevance Features}

There are two challenges to using geographic features. First we do not 
know where the event is and second most sentences do not contain references
to a location.
We address the first issue by extracting all locations from sentences at the
current hour and looking up their latitude and 
longitude using a publicly available geolocation service. Since the document
stream contains documents that are at least somewhat relevant to the event,
we assume in aggregate the locations should give us a rough area of interest.
The locations are clustered (using affinity propagation and uniform salience)
and we treat the resulting cluster centers
as the event locations for the current time.

@@

\paragraph{Temporal Relevance Features}

Our data consists of hourly crawls of online content and so we exploit the temporality of corpus by capturing the burstiness of a sentence, i.e.  the change in word frequency from one hour to the next.``Bursty'' sentences often indicate new and important data.

We compute the IDF for each hour in our data stream. 
For each sentence, the average TFIDF for the current hour $t$ is taken as a 
feature. Additionally, we use the difference in average TFIDF from time $t$
to $t-i$ for $i = \{1, \ldots, 24\}$ to measure how the TFIDF scores for the 
sentence have changed over the last 24 hours.

>>>>

Our update summarization system takes as input 
\begin{enumerate*}[label=\itshape\alph*\upshape)]
  \item a short query defining the event to be tracked (e.g. `Hurricane Sandy'), 
  \item an event category defining the type of event to be tracked (e.g. `hurricane'), 
  \item a stream of time-stamped documents %, $(\doc_0, \doc_1,\ldots,\doc_T)$,
  presented in temporal order, and \item an evaluation time period of interest.
    %  $(\stime,\etime)$.  
\end{enumerate*} 
While processing documents
throughout the time period of interest, the system outputs sentences
from these documents likely to be useful to query issuer.  We refer
to these selected sentences as \emph{updates}.

In order to measure the usefulness of a system's updates, we consider
the degree to which the system output reflects the different
aspects of an event.  Events are often composed of a variety of sub-events.  
For example, the Hurricane Sandy
event includes sub-events related to the storm making landfall,
the ensuing flooding, the many transportation issues, amongst many
others.  An ideal system would update the user about each of these
sub-events as they occur, with low latency.  In order to use
language consistent with previous literature, we refer to these
sub-events as the \emph{nuggets} associated with an event.  Nuggets are
defined as a fine-grained atomic sub-event associated with an event.  
We present several example nuggets associated with the Hurricane
Sandy event in Figure \ref{fig:nuggets}.  We describe how these 
nuggets are found in Section \ref{sec:data}.

% Updates should not only be relevant to the event but also salient,
% i.e. worthy of
% reporting.
% For most domains, updates also need to be
% timely and novel, i.e. users need to be informed of changes in the
% event as quickly as possible.
% Finally, in aggregate the updates must comprehensively summarize the
% event.

@@

Throughout our treatment of our algorithm, the \emph{salience} 
of an update captures the degree to which it reflects an 
event's nuggets.  Assuming that we have a text representation 
of our nuggets, the salience of an update $u$  with respect to a set of nuggets $N$ is
defined as,
\begin{align}
\operatorname{salience}(u) = \operatorname{max}_{n \in N} 
\operatorname{sim}(u, n) \ref{eq:salience}
\end{align}
where $\operatorname{sim}(\cdot)$ is the semantic similarity such as
the cosine similarity of latent vectors associated with the update and 
nugget text \cite{?}. % We train
% a regression model to predict salience using features derived from
% the updates themselves
% and the document stream.

@@

Our system architecture follows a simple pipeline design where each
stage provides an additional level of processing or filtering of the input
sentences.
We begin with an empty update summary $U$.
At each hour we receive a new batch of sentences $b_t$ from the stream
and perform the following actions:
\begin{enumerate}
    \item predict the salience of sentences in $b_t$ (Section~\ref{sec:salpred}),
  \item select a set of exemplar sentences  in $b_t$ by combining clustering with 
      salience predictions (Section~\ref{sec:exsel}),
  \item add the most novel and salient exemplars to $U$ (Section~\ref{sec:upsel}).
\end{enumerate}

The resultant list of updates $U$ is our summary of the event.
% Step 2 uses the affinity propagation algorithm to incorporate the salience
% predictions from step 1. We refer to this summarization
% system as the \textbf{AP+Salience} model.

@@

When evaluating our summarization system
we do not have access to event nuggets. However, we can use the nuggets
in our training data to learn a model to predict salience for sentences
in new events.
For each event in our training data, we sample a set of sentences and  each 
sentence's salience is computed according to Equation \ref{eq:salience}.
This results in training set of set sentences and the target values 
(their salience) to predict.

@@

\fdcomment{stress here that this technique can be applied in situations beyond crisis; any situation where the
expected summary is similar to some previously seen target or some side information.}

@@

\paragraph{Geographic Relevance Features}
\fdcomment{need introduction here.  what are geographic features?}
There are two challenges to using geographic features. First we do not 
know where the event is and second most sentences do not contain references
to a location.
We address the first issue by extracting all locations from sentences at the
current hour and looking up their latitude and 
longitude using a publicly available geolocation service. 
\fdcomment{is this all documents in the bucket or the filtered set?  is it a biased sample?}
Since the document
stream contains documents that are at least somewhat relevant to the event,
we assume in aggregate the locations should give us a rough area of interest.
The locations are clustered (using affinity propagation and uniform salience)
\fdcomment{affinity propagation undefined}
and we treat the resulting cluster centers
as the event locations for the current time.

@@

\paragraph{Temporal Relevance Features}
\fdcomment{motivate burstiness; explain what it is before using the expression.}
Our data consists of hourly crawls of online content and so we exploit the temporality of corpus by capturing the burstiness of a sentence, i.e.  the change in word frequency from one hour to the next.``Bursty'' sentences often indicate new and important data.

We compute the IDF for each hour in our data stream. 
For each sentence, the average TFIDF for the current hour $t$ is taken as a 
feature. Additionally, we use the difference in average TFIDF from time $t$
to $t-i$ for $i = \{1, \ldots, 24\}$ to measure how the TFIDF scores for the 
sentence have changed over the last 24 hours. \fdcomment{unclear.  is it just changing the IDF part of the 
items in the average?}
